---
title: ""
author: ""
date: ""
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    smooth_scroll: false
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(reshape2)
library(tidyverse)
library(rtracklayer)
library(ggrepel)
library(ggplot2)
library(dplyr)
library(GenomicRanges)
library(reactable)
library(data.table)
#
library(DESeq2)
#
library(plotly)
#
library(TxDb.Mmusculus.UCSC.mm10.knownGene)
library(org.Mm.eg.db)
library(ChIPseeker)
#
txdb <- TxDb.Mmusculus.UCSC.mm10.knownGene
#
options(ChIPseeker.ignore_1st_exon = TRUE)
options(ChIPseeker.ignore_1st_intron = TRUE)
options(ChIPseeker.ignore_downstream = TRUE)
options(ChIPseeker.ignore_promoter_subcategory = TRUE)
```

# Table of overlap

## K36me2 {.tabset .tabset-pills}

### TKO vs. PA
```{r,table_ol_K36me2_TKO_PA,echo = FALSE, out.width = "100%", fig.align = "default",message=FALSE,warning=FALSE}
df <- read.csv("~/Documents/10T_K36me2/data/overlap.tables/TKO_cf_PA.ATACseq.K36me2.csv") %>%
  column_to_rownames("X")
reactable(df)
```

### QKO vs. PA
```{r,table_ol_K36me2,echo = FALSE, out.width = "100%", fig.align = "default",message=FALSE,warning=FALSE}
df <- read.csv("~/Documents/10T_K36me2/data/overlap.tables/QKO_cf_PA.ATACseq.K36me2.csv")
reactable(df)
```

### QKO vs. TKO
```{r,table_ol_K36me2_QKO_TKO,echo = FALSE, out.width = "100%", fig.align = "default",message=FALSE,warning=FALSE}
df <- read.csv("~/Documents/10T_K36me2/data/overlap.tables/QKO_cf_TKO.ATACseq.K36me2.csv")
reactable(df)
```

## K9me3 {.tabset .tabset-pills}

### TKO vs. PA
```{r,table_ol_K9me3,echo = FALSE, out.width = "100%", fig.align = "default",message=FALSE,warning=FALSE}
df <- read.csv("~/Documents/10T_K36me2/data/overlap.tables/TKO_cf_PA.ATACseq.K9me3.csv") %>%
  column_to_rownames("X")
reactable(df)
```

---

# Distribution {.tabset .tabset-pills}

## TKO vs. PA
```{r,ATAC_seq_distribution_TKO_cf_PA,echo = FALSE, out.width = "100%", fig.align = "default",message=FALSE,warning=FALSE}
load("~/Documents/10T_K36me2/data/differential.ATACseq.regions/distributions/TKO_cf_PA.ATAC.distribution.RData")
plotAnnoBar(peak_ann)
```

## QKO vs. PA
```{r,ATAC_seq_distribution_QKO_cf_PA,echo = FALSE, out.width = "100%", fig.align = "default",message=FALSE,warning=FALSE}
load("~/Documents/10T_K36me2/data/differential.ATACseq.regions/distributions/QKO_cf_PA.ATAC.distribution.RData")
plotAnnoBar(peak_ann)
```

## QKO vs. TKO
```{r,ATAC_seq_distribution_QKO_TKO,echo = FALSE, out.width = "100%", fig.align = "default",message=FALSE,warning=FALSE}
load("~/Documents/10T_K36me2/data/differential.ATACseq.regions/distributions/QKO_cf_TKO.ATAC.distribution.RData")
plotAnnoBar(peak_ann)
```

---

# ChIP signal {.tabset .tabset-pills}

## TKO vs. PA {.tabset .tabset-pills}

### ATAC {.tabset}

#### All
```{r,heatmap_TKO_cf_PA,echo = FALSE,fig.show = "hold", out.width = "33%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_K36me2/images/TKO_cf_PA_log2FC_3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

#### Promoter vs. IGR
```{r,heatmap_TKO_cf_PA.IGR_Promoter,echo = FALSE,fig.show = "hold", out.width = "100%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_K36me2/images/TKO_cf_PA_log2FC_3/promoter_cf_IGR", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## QKO vs. PA
```{r,heatmap_QKO_cf_PA,echo = FALSE,fig.show = "hold", out.width = "33%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_K36me2/images/QKO_cf_PA_log2FC_3", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

## QKO vs. TKO
```{r,heatmap_QKO_cf_TKO,echo = FALSE,fig.show = "hold", out.width = "33%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_K36me2/images/QKO_cf_TKO_log2FC_2", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

---

# Enhancers {.tabset .tabset-pills}

## Overlap {.tabset}

### TKO vs. PA
```{r,table_ol_K36me2_TKO_PA_enh,echo = FALSE, out.width = "100%", fig.align = "default",message=FALSE,warning=FALSE}
df <- read.csv("~/Documents/10T_K36me2/data/overlap.tables/TKO_cf_PA.ATACseq.enhancers.csv")
reactable(df)
```

### QKO vs. PA
```{r,table_ol_K36me2_QKO_PA_enh,echo = FALSE, out.width = "100%", fig.align = "default",message=FALSE,warning=FALSE}
df <- read.csv("~/Documents/10T_K36me2/data/overlap.tables/QKO_cf_PA.ATACseq.enhancers.csv")
reactable(df)
```

### QKO vs. TKO
```{r,table_ol_K36me2_QKO_TKO_enh,echo = FALSE, out.width = "100%", fig.align = "default",message=FALSE,warning=FALSE}
df <- read.csv("~/Documents/10T_K36me2/data/overlap.tables/QKO_cf_TKO.ATACseq.enhancers.csv")
reactable(df)
```

## Heatmaps {.tabset}

### TKO vs. PA
```{r,heatmap_TKO_cf_PA_enhancer,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_K36me2/images/TKO_cf_PA.enhancer", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

### QKO vs. PA
```{r,heatmap_QKO_cf_PA_enhancer,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_K36me2/images/QKO_cf_PA.enhancer", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```

### QKO vs. TKO
```{r,heatmap_QKO_cf_TKO_enhancer,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
imageList <- list.files("~/Documents/10T_K36me2/images/QKO_cf_TKO.enhancer", pattern= "*.png", full.names=T)
include_graphics(imageList,dpi = 600)
```