---
title: ""
author: ""
date: ""
output:
  html_document:
    toc_float: false 
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Homer motif analysis {.tabset .tabset-pills}

## TKO vs. PA {.tabset .tabset-pills}

### Open {.tabset}

#### All

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/TKO_cf_PA_logFC_3/HOMER.out/open_peaks.all/knownResults.open_peaks.html")
```

#### Promoter

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/TKO_cf_PA_logFC_3/HOMER.out/open_peaks.promoter/knownResults.html")
```

#### Intron

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/TKO_cf_PA_logFC_3/HOMER.out/open_peaks.intron/knownResults.html")
```

#### Intergenic

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/TKO_cf_PA_logFC_3/HOMER.out/open_peaks.intergenic/knownResults.html")
```

### Closed {.tabset}

#### All

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/TKO_cf_PA_logFC_3/HOMER.out/closed_peaks.all/homer.motifs.out.closed.peaks/knownResults.closed_peaks.html")
```

#### Promoter

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/TKO_cf_PA_logFC_3/HOMER.out/closed_peaks.promoter/knownResults.html")
```

#### Intron

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/TKO_cf_PA_logFC_3/HOMER.out/closed_peaks.intron/knownResults.html")
```

#### Intergenic

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/TKO_cf_PA_logFC_3/HOMER.out/closed_peaks.intergenic/knownResults.html")
```

--- 

## QKO vs. PA {.tabset .tabset-pills}

### Open {.tabset}

#### All

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_PA_logFC_3/HOMER_res/open_peaks.all/knownResults.html")
```

#### Promoter

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_PA_logFC_3/HOMER_res/open_peaks.promoter/knownResults.html")
```

#### Intron

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_PA_logFC_3/HOMER_res/open_peaks.intron/knownResults.html")
```

#### Intergenic

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_PA_logFC_3/HOMER_res/open_peaks.intergenic/knownResults.html")
```

### Closed {.tabset}

#### All

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_PA_logFC_3/HOMER_res/closed_peaks.all/knownResults.html")
```

#### Promoter

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_PA_logFC_3/HOMER_res/closed_peaks.promoter/knownResults.html")
```

#### Intron

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_PA_logFC_3/HOMER_res/closed_peaks.intron/knownResults.html")
```

#### Intergenic

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_PA_logFC_3/HOMER_res/closed_peaks.intergenic/knownResults.html")
```

---

## QKO vs. TKO {.tabset .tabset-pills}

### Open {.tabset}

#### All

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_TKO_logFC_2/HOMER_res/open_peaks.all/knownResults.html")
```

#### Promoter

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_TKO_logFC_2/HOMER_res/open_peaks.promoter/knownResults.html")
```

#### Intron

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_TKO_logFC_2/HOMER_res/open_peaks.intron/knownResults.html")
```

#### Intergenic

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_TKO_logFC_2/HOMER_res/open_peaks.intergenic/knownResults.html")
```

### Closed {.tabset}

#### All

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_TKO_logFC_2/HOMER_res/closed_peaks.all/knownResults.html")
```

#### Promoter

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_TKO_logFC_2/HOMER_res/closed_peaks.promoter/knownResults.html")
```

#### Intron

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_TKO_logFC_2/HOMER_res/closed_peaks.intron/knownResults.html")
```

#### Intergenic

```{r,warning=FALSE,echo=FALSE,collapse=TRUE}
htmltools::includeHTML("~/Documents/10T_K36me2/data/differential.ATACseq.regions/QKO_cf_TKO_logFC_2/HOMER_res/closed_peaks.intergenic/knownResults.html")
```
